\section*{Thanks}
From Kyushu University, I would like to thank teacher Hiroyasu Sakamoto for his excellent supervision throughout my stay in the laboratory, and his tremendous help both in and outside laboratory work. I would also like to thank all the laboratory members for their help, bouncing ideas off of each others, and for making the effort of speaking in English with me. Many thanks to the people at the support center and in particular Chitose Oka for her help with accommodations and the English school.

From UTBM, I would like to thank Japanese language teacher Keiko Jimbo, for being a great teacher and a tremendous help finding this internship in the first place. Yassine Ruichek and Cindy Capelle for teaching me nearly everything I know about image processing and machine learning. Mireille Jacquot for being very patient and understanding both during my internship search and during my stay in Japan.

In France, I would like to thank my family for its enormous support, and trusting me in my choices and decisions. The French government and the province of Franche-Comté for their financial help. Special thanks goes to the group whose name changes every month for its support in the more difficult times.

In Japan, I would like to thank the very many friends I met there, and made my stay there an incredible experience. Special thanks go to Jelle Postma, Ketty Chung and Giorgia Sassi for helping provide plenty of Japanese animation material. Yuki Nakagawa, for being a great supporter and being there whenever I needed his help. Patxi Garcia Novo, for his help with the scholarship application and allowing me to crash on his couch for $2$ weeks. Everyone from Ijiri dorm and all the Japanese friends I haven't mentioned, you guys are awesome and I enjoyed hanging out with you all.
